Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-21 draft/ms_v4.tex
Alexie's edits and Add Jean Coupon to author list

% Version 0; Rough outline by SH
% Version 1; First draft by SH
% Version 2; Finish main text; with edits from Susan Foster
% Version 3; More edits from Susan

@@

@@

%% ------------------------------------------------------------------------------------ %%
\title{HSC Synthetic Pipeline I: Basic Design and Characterization of HSC
       Photometric Performance}

\author{Song Huang \altaffilmark{1,2}
        Alexie Leauthaud \altaffilmark{1,2},
        Ryoma Murata \altaffilmark{1, 4},
        Jim Bosch \altaffilmark{3},
        Paul Price \altaffilmark{3},
        Robert Lupton \altaffilmark{3},
        Rachel Mandelbaum \altaffilmark{5},
        Claire Lackner \altaffilmark{1},
        Steven Bickerton \altaffilmark{1},
        Satoshi Miyazaki \altaffilmark{6}
        HSC Collaboration \altaffilmark{7}}
%% ------------------------------------------------------------------------------------ %%

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the
    Universe, The University of Tokyo Institutes for Advanced Study,
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}

\altaffiltext{2}{Department of Astronomy and Astrophysics, University of California,
    Santa Cruz, 1156 High Street, Santa Cruz, CA 95064 USA}

@@

\altaffiltext{7}{Other affiliations}

@@

    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope.
    As SSP reaches to detection limit of $i>26.0$ mag in the Wide field, it is
    challenging to achieve accurate, unbiased, and consistent photometry across all
    five bands.
    To improve data processing and achieve accurate photometric measurements, we have
    developed \synpipe{}, a \texttt{Python}-based, flexible framework that interfaces
    with the HSC data reduction pipeline (\hscpipe{}) to process data from the first
    public HSC--SSP data release.
    In the first paper of this series, we explain the design and implementation of
    \synpipe{}, and use \coadd{} images in two Wide layer \tracts{} with representative
    seeing conditions to examine the photometric performance of \hscpipe{}.
    We find that uncertainties of HSC \forced{} PSF photometry for stars typically
    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
    mag (1\%-7\% accuracy in the $i$-band).
    For synthetic galaxies based on a single-\ser{} model, uncertainties of the
    forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag
    to 0.20 mag at $i{\sim} 25.2$ mag.
    Over the color and magnitude ranges used in these \synpipe{} tests, we find that
    both \forced{} PSF and \cmodel{} photometry provide unbiased color estimates
    that are robust in different seeing conditions.
    We also notice a few issues in the current \hscpipe{} that are worth keeping
    in mind when using HSC data:
    1) The degree to which an object is blended with others impacts the photometric
    accuracy, especially for point sources.
    Highly blended objects tend to have larger photometric uncertainty, systematically
    underestimated flux, and slightly biased color.
    2) A relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
    misclassified as extended objects.
    3) The shape and size estimates for galaxies using \cmodel{} suffer from strong
    biases.

@@

    %% Background
    Wide-field, multi-band imaging surveys have stepped onto the central stage of
    modern astrophysics and cosmology over the past decade.
    They also have a bright future on many current and planned ambitious projects,
    such as the Large Synoptic Survey Telescope
    (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
    Telescope
    (WFIRST; \citealt{Dressler2012})\footnote{\url{https://wfirst.gsfc.nasa.gov/}},
    and the \textit{Euclid} project
    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}.
    Among many ongoing efforts, the Subaru Strategic Program
    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}, which
    uses the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
    the Subaru telescope, is the most efficient in terms of
    etendue\footnote{The collecting area multiplied by the field of view.}.
    Together, these surveys will greatly help us test cosmological models, trace the
    evolution of galaxies, study the stellar structure of our Milky Way, and discover
    a large number of interesting transient objects.

    %% Challenges
    Before we can tackle any outstanding scientific questions, we must first learn
    how to handle the huge amount of data\footnote{Right now, SSP has accumulated
    ${\sim}300$ TB of data products.} generated by these projects as well as achieve
    accurate photometric measurements of different types of objects.
    Data handling becomes increasingly challenging in the age of modern imaging
    surveys, in part due to variations and effects related to the cameras'
    charge-coupled devices (CCDs).
    The cameras are often made up of multiple CCDs, each with slightly different
    characteristics, and have large fields-of-view (FoV) over not perfectly flat
    focus planes.
    During observation, the seeing and background conditions always show spatial
    and temporal variations across the FoV.
    The full-depletion, thick CCDs selected for the cameras enable long exposure
    times and excellent sensitivity in the red-end, but they often suffer from the
    so-called ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that
    brighter stars appear larger than they are.
    These variations and effects make accurate astrometric and photometric calibration,
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g., \citealt{Schlafly2012}).
    The multi-epoch, multi-band nature of the surveys also complicate data reduction
    because the scientist must pay special attention to image stacking, multi-band
    object detection, and measurement processes.
    Furthermore, as ongoing surveys reach to increasingly deeper detection limit
    (e.g., SSP Wide reaches to $5\ \sigma$ detection limit of point source of
    ${\sim}26.4$ mag), the number of objects in a unit area, especially faint objects,
    becomes much higher.
    In addition, it is much more common to observe objects that overlap each other at
    different levels (a phenomenon often referred to as ``blended'').
    These modern imaging survey challenges call for photometric measurement methods
    that are more powerful and precise than those used in previous, shallower surveys.

%% ------------------------------------------------------------------------------------ %%
    %% Reason
    The challenges are not merely technical details; their resolution is crucial
    to achieving the surveys' key scientific goals.
    For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001})
    is a powerful tool for measuring the large-scale distribution of dark matter and
    following its evolution.
    However, WL measurements critically depend on the ability to model PSF and measure
    the shape of background galaxies with high precision
    (e.g., \citealt{Mandelbaum2015}).
    The photometric redshift measurement (e.g., \citealt{Benitez2000, Bolzonella2000,
    Ilbert2009}) is fundamentally important for studying the evolution of galaxies,
    and the ``drop-out'' method is very useful in selecting high-redshift galaxies
    (e.g., \citealt{Steidel1996}).
    However, both of those methods are based on accurate multi-band photometric
    measurements.
    There are many other examples, but these are sufficient to demonstrate that we
    need to develop new frameworks to oversee the data reduction process of modern
    imaging surveys.
    Several tools with similar goals have been developed (e.g., \citealt{Chang2015,
    Suchyta2016}) for the Dark Energy Survey (DES; \citealt{DES2005}).
    As for the HSC--SSP (hereafter referred to as the HSC survey), the higher quality
    images and more complex \hscpipe{} also require more carefully designed tool to
    test them.

    %% Organization
    Here, we present \synpipe{}, a \texttt{Python}-based software that is a flexible
    framework with many applications that can help future developments of the HSC data
    reduction pipeline (\hscpipe{}).
    Below, we briefly introduce the HSC survey and the current status of data
    reduction (Section \ref{sec:ssp}), explain \synpipe{} design and implementation
    (Section \ref{sec:synpipe}), and demonstrate \synpipe{} usage via straightforward
    tests (Section \ref{sec:test}) that focus on the general photometric quality for
    both synthetic stars and galaxies (Section \ref{sec:result}).
    We then summarize the work and discuss future developments in
    Section \ref{sec:summary}.

    The \synpipe{} code, along with basic documents and a few examples, is available
    on GitHub at: \texttt{https://github.com/dr-guangtou/synpipe}.
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of \synpipe{} basic procedures.
        Gray boxes indicate the required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects
        simulated images of synthetic objects onto a single-frame image.
        We show an example CCD image with and without synthetic objects on it
        (highlighted by green circles).
        Red boxes depict the subsequent image coadding and multiband measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}.
        We show a small piece of \coadd{} image with synthetic objects on it.
        The figure on the right side of the middle row shows the spatial relation
        between \tract{} (outlined by the black dashed lines; each small region
        is a \texttt{Patch}) and all the \visits{} that contribute to it.
        (Each \visit{} has a  unique color; each small region is the size of a CCD.)
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2--m Subaru telescope,
    the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broad bands
    ($grizy$; Kawanomoto\etal in prep.).
    The Deep (four separated fields; ${\sim}27$ deg$^2$) and UltraDeep (two separated
    fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters
    and employ a slightly different surveying strategy.
    Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the
    HSC collaborators.

    The HSC camera (\citealt{Miyazaki2012}) is made up of 124 full-depletion thick
    CCDs: 112 for science and another 12 for guiding and focusing.
    The camera has a circular FoV with a 1.5 deg diameter.
    Each CCD contains 2048$\times$4096 pixels distributed in four amplifiers.
    The pixel size is equal to 0.168\asec{} on the sky.

    In February 2017, the HSC collaboration released the first 1.7 years of data to
    the public (DR1;
    \citealt{HSCDR1})\footnote{\texttt{https://hsc-release.mtk.nao.ac.jp }}.
    For our work, we focused on data from the Wide layer as they relate to key
    scientific goals of the HSC survey, which include WL cosmology, galaxy evolution
    since $z{\sim}1$, and studies of galaxy clusters.
    The current Wide layer includes ${\sim}108$ deg$^2$ of sky isolated in
   six different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purposes.}.
    Except for the HECTOMAP field, the regions are all close to the equator.
    In the Wide layer, the $g$ and $r$ bands have 10 mins of exposure broken into four
    dithers\footnote{Large, ${\sim}1/3$ of the FoV dither pattern is used to ensure
    uniform coverage.}; for the remaining three bands, 20 mins of exposure time and six
    dithers are used\footnote{Several 30 s exposures are taken to improve the
    dynamic range.}.
    The survey prioritizes the observations so that the $i$-band can have excellent
    seeing conditions to help make accurate WL shape measurements.
    The current Wide layer has impressive median seeing with FWHM${\sim}0.6$\asec{},
    and has a $i{\sim} 26.4$ mag $5\sigma$ point source detection limit.
    \citealt{HSCDR1} provides details on the first data release and data status.

@@

    The HSC survey data are currently reduced by \hscpipe{} \texttt{v4.0.5}, a
    version of the LSST reduction pipeline (\citealt{Ivezic2008, Axelrod2010,
    Juric2015}), which is described in detail in Bosch\etal (in prep.).
    Since \synpipe{} is intrinsically connected to the complex data reduction
    processes in \hscpipe{}, we briefly introduce the main steps below, along with
    a few key HSC/LSST terms.

@@

        \item \textbf{Single-\texttt{Visit~}Processing}:
            Each individual exposure is called a \term{Visit} and is assigned
            an even integer.
            After initial data screening (in background, seeing, and transparency
            Furusawa\etal in prep.), \hscpipe{} detrends these data (subtraction
            of overscan, bias, and dark; flatfielding), generates variance and mask
            images, subtracts background, and provides initial astrometric and
            photometric calibrations.
            \textbf{\synpipe{} will use the spatially varying PSF models, photometric
            zeropoints, and the World Coordinate System (WCS; \citealt{WCS1, WCS2})
            corrected for optical distortion.}.

        \item \textbf{Multi-\visit{} Processing}:
            After single-\visit{} processing, \hscpipe{} warps and mosaics the
            reduced CCD images into much deeper \coadd{} images while improving
            the astrometric and photometric calibrations via processes similar to
            the \"{u}ber-calibration in the Sloan Digital Sky Survey (SDSS)
            \citep{Padmanabhan2008}.
            \textbf{\synpipe{} will use these improved calibrations.}
            \hscpipe{} organizes these \coadd{} images into equiareal rectangular
            regions, or \tracts{}, which are predefined as iso-latitude tessellations.
            One \tract{} covers approximately $1.7\times 1.7$ deg$^2$ of sky, and
            adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
            Each \tract{} is further divided into $9\times9$ \texttt{Patches}.
            A \texttt{Patch} is a $4200\times4200$ pixels rectangular region, and
            adjacent \texttt{Patches} overlap each other by 100 pixels.
            \textbf{The \tract{} and \texttt{Patch} are basic units to deal
            with HSC \coadd{} images and \synpipe{} tests.}

        \item \textbf{Multi-band Measurements}:
            To achieve consistent photometry across all filters, \hscpipe{} first
            detects and deblends objects on \coadd{} images in each band
            independently (the \unforced{} measurements).
            The collection of above-threshold pixels for each object is referred to as
            a \texttt{footprint}.
            \hscpipe{} merges the \texttt{footprints} and flux peaks in the different
            bands and then selects a reference band for each object based on its $S/N$
            in each band (usually it is the $i$-band).
            With the centroids, shape, and other non-amplitude parameters fixed at the
            reference values, \hscpipe{} performs \forced{} photometry, which is
            optimized to generate accurate colors.

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain a variety of
            photometric information (see \citealt{HSCDR1} for details).
            \textbf{Here, we focus on the \forced{} \texttt{psf} and \cmodel{}
            photometry.}
            \texttt{psf} photometry should provide the most appropriate magnitudes and
            colors for point sources.
            Improved over the SDSS version (\citealt{Lupton2001, Abazajian2004}),
            the HSC \cmodel{} algorithm (described in Bosch\etal, in prep.) fits
            each object's flux distribution using a combination of the de Vaucouleurs
            profile and an exponential component that takes the PSF convolution
            into account.
            \cmodel{} is designed to yield accurate colors for galaxies.
            In addition, the star--galaxy classification task is performed based on
            the difference between the \texttt{psf} and \cmodel{}{} magnitudes.

    DR1 data quality has been vetted in \citet{HSCDR1} via cross-checking
    with the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1
    imaging survey (\citealt{Schlafly2012, Tonry2012, Magnier2013}) to examine the
    behaviors of the stellar sequence and the shape of the PSF models.
    Generally speaking, the PSF photometry is accurate to 1--2\% level, and the
    astrometry is accurate to ${\sim}10$ and 40 max internally and externally.

@@

%% ------------------------------------------------------------------------------------ %%
\subsection{ \synpipe{} Basic Design}
    \label{ssec:design}

    \hscpipe{} is a complex data reduction pipeline that still faces many challenges
    and is under active development.
    Unlike most photometric pipelines on the market, it involves high-level reduction
    processes that produce not only deep \coadd{} images but also a series of
    science-ready catalogs.
    To faithfully test \hscpipe{} and the related data products, we have designed an
    approach that ensures \synpipe{} satisfies a few basic standards:

@@

        \item \textbf{Realistic Images}:
            Instead of using the fully generative approach to simulate full HSC-like
            images from the ground up (e.g., \citealt{Chang2015}), \synpipe{} injects
            synthetic objects into the observed image so that all the realistic
            features of the real data (e.g., blended objects; proximity to bright
            objects, bleeding trails, other optical artifacts can be included in the
            test.
            The impact of these features can be important to any topic (e.g., WL
            analysis; stellar mass function of galaxies) that cares about the selection
            function and completeness of samples.
            In \synpipe{}, point source is simulated using the HSC PSF model,
            and a realistic galaxy model is created by the modular galaxy image
            simulation toolkit, \galsim{} (\citealt{Rowe2015})
            \footnote{\texttt{https://github.com/GalSim-developers/GalSim}}.

>>>>

% Version 0; Rough outline by SH
% Version 1; First draft by SH
% Version 2; Finish main text; with edits from Susan Foster
% Version 3; More edits from Susan
% Version 4; Edits from Alexie

@@

\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}

@@

%% ------------------------------------------------------------------------------------ %%
\title{Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.}

\author{Song Huang \altaffilmark{1,2}
        Alexie Leauthaud \altaffilmark{1,2},
        Ryoma Murata \altaffilmark{2, 4},
        Jim Bosch \altaffilmark{3},
        Paul Price \altaffilmark{3},
        Robert Lupton \altaffilmark{3},
        Rachel Mandelbaum \altaffilmark{5},
        Claire Lackner \altaffilmark{2},
        Steven Bickerton \altaffilmark{2},
        Satoshi Miyazaki \altaffilmark{6}, 
        Jean Coupon \altaffilmark{7},
        HSC Collaboration \altaffilmark{8}}
%% ------------------------------------------------------------------------------------ %%

\altaffiltext{1}{Department of Astronomy and Astrophysics, University of California,
    Santa Cruz, 1156 High Street, Santa Cruz, CA 95064 USA}

\altaffiltext{2}{Kavli Institute for the Physics and Mathematics of the
    Universe, The University of Tokyo Institutes for Advanced Study,
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}

@@

\altaffiltext{7}{Department of Astronomy, University of Geneva, ch. d'\'Ecogia 16, 
    1290 Versoix, Switzerland}

\altaffiltext{8}{Other affiliations}

@@

    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope. The  Wide layer of the SSP is both wide and deep, reaching a detection limit of $i>26.0$ mag. At these depths, it is challenging to achieve accurate, unbiased, and consistent photometry across all
    five bands. The HSC data are reduced using a pipeline that builds on the prototype pipeline being designed by the Large Synoptic Survey Telescope’s Data Management system. We have developed a \texttt{Python}-based, flexible framework to inject synthetic galaxies into real HSC images called \synpipe{}. In this paper, we explain the design and implementation of \synpipe{} and we generate a sample of synthetic galaxies to examine the photometric performance of the HSC pipeline. For stars, we achieve 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at $i{\sim}25.5$ in the $i$-band (corresponding to uncertainties of ${\sim}0.01$ and ${\sim}0.06$ mag respectively). \alexie{Put numbers in here using this phrase format} For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry achieves 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at $i{\sim}25.5$ in the $i$-band (corresponding to uncertainties of ${\sim}0.01$ and ${\sim}0.06$ mag respectively). 
    %For synthetic galaxies based on a single-\ser{} model, uncertainties of the
    %forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag
    %to 0.20 mag at $i{\sim} 25.2$ mag.
    we show that
    both \forced{} PSF and \cmodel{} photometry yield unbiased color estimates
    that are robust to seeing conditions. We identify several caveats that apply to version xxx of the  HSC pipeline and than need to be considered when using data from the first public HSC data release. First, the degree to which an object is blended with other objects impacts the overall photometric performance.  This is especially true for point sources \alexie{quanityf here}. Highly blended objects tend to have larger photometric uncertainties, systematically underestimated fluxes \alexie{Should be overestimated here no?}, and slightly biased colors. Second, a relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
    misclassified as extended objects \alexie{need to quantify here}. Third, the shape and size estimates for galaxies using \cmodel{} suffer from strong
    biases \alexie{quantify here}.

@@

    %% Background
    Wide-field, multi-band imaging surveys have stepped onto the central stage of
    modern astrophysics and cosmology over the past decade.  These efforts will soon be replaced with even more ambitious programs such as the Large Synoptic Survey Telescope
    (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
    Telescope
    (WFIRST; \citealt{Dressler2012})\footnote{\url{https://wfirst.gsfc.nasa.gov/}},
    and the \textit{Euclid} project
    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}. Among many ongoing efforts, the Subaru Strategic Program
    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}, which
    uses the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
    the Subaru telescope, is the most efficient in terms of
    etendue\footnote{The collecting area multiplied by the field of view.}. Surveys such as HSC, and other to follow, will  provide stringent constraints on  the cosmological model,  characterize the evolution of galaxies, map out the stellar structure of our Milky Way, and are poised to discover a large number of interesting transient objects.

    %% Challenges
    Before we can tackle outstanding scientific questions, we must first learn
    how to handle the the large amounts of data\footnote{Right now, SSP has accumulated
    ${\sim}300$ TB of data products.} generated by these projects while satisfying  strict requirements for  high quality image processing with accurate measurement for the magnitudes and shapes of stars and galaxies. Data handling becomes increasingly challenging in the age of modern imaging
    surveys am we aim to characterize and account for subtle effects related to charge-coupled devices (CCDs). Cameras are made up of multiple CCDs, each with slightly different
    characteristics, and have large fields-of-views (FoV) over focal planes that are not perfectly flat. During observations, the seeing and background conditions display spatial and temporal variations across the FoV. The full-depletion, thick CCDs selected for HSC enable long exposure
    times and have excellent red-sensitivity, but they also suffer from the
    so-called ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that
    brighter stars have larger Point Spread Functions (PSFs) than fainter stars. These variations and effects make accurate astrometric and photometric calibration,
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g., \citealt{Schlafly2012}). Furthermore, as surveys reach to increasingly deeper detection limits
    (e.g., the SSP Wide layer reaches a $5\ \sigma$ point source detection limit of
    ${\sim}26.4$ mag), the number of objects per unit area increases.  Hence, deep surveys become  more sensitive and subject to the effects of blending.  The challenge of modern imaging surveys call for  photometric measurement methods
    that are more powerful and precise than those used in previous, shallower surveys.

    %

    These challenges are not merely technical details; their resolution is crucial
    to achieving key scientific goals.
    For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001})
    is a powerful tool for measuring the large-scale distribution of dark matter.
    However, WL measurements critically depend on our ability to measure the shape and photometric redshifts of background galaxies with high precision. Photometric redshifts (e.g., \citealt{Benitez2000, Bolzonella2000,
    Ilbert2009}) are fundamentally important for studying the evolution of galaxies,
    and the ``drop-out'' method is critical for selecting high-redshift galaxies
    (e.g., \citealt{Steidel1996}).
    However, both of those methods reply on the availability of accurate multi-band photometric
    measurements. With increasingly large surveys,  and with more stringent requirements on data quality,  quality control also becomes a pressing issue.

   In this paper, we present a \texttt{Python}-based software package called  \synpipe{} that  injects synthetic objects into  HSC images  and  which interfaces with the HSC data reduction pipeline (\hscpipe{}). Among other applications, \synpipe{} can be used to perform quality control and to characterize the performance and limitations of  \hscpipe{}. Several tools with similar goals have been developed (e.g., \citealt{Chang2015,
    Suchyta2016}) for the Dark Energy Survey (DES; \citealt{DES2005}).

 \alexie{Edit here following this format}. In Section 1 we ... in section 2 we ....

    Below, we briefly introduce the HSC survey and the current status of data
    reduction (Section \ref{sec:ssp}), explain \synpipe{} design and implementation
    (Section \ref{sec:synpipe}), and demonstrate \synpipe{} usage via straightforward
    tests (Section \ref{sec:test}) that focus on the general photometric quality for
    both synthetic stars and galaxies (Section \ref{sec:result}).
    We then summarize the work and discuss future developments in
    Section \ref{sec:summary}.

    The code for \synpipe{}, along with documentation and examples, is made available
    on GitHub at: \texttt{https://github.com/dr-guangtou/synpipe}.

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of the main steps involved in using \synpipe{}.
        Gray boxes indicate required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects synthetic objects into single-frame images. Below the blue box, we show an HSC image before and after the insertion of synthetic galaxies. The positions of synthetic  objects are highlighted with green circles. Red boxes depict the image coadding and multi-band measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py}. At the bottom left, we show a \coadd{} image which contains synthetic galaxies. On the right hand side, we show the spatial relation
        between \texttt{Tracts}, \texttt{Patches}, and \texttt{Visits}. The xxxxxxx colored box corresponds to one \texttt{Tract} which has an area of about xx deg$^2$. Large colored circles are \texttt{Visits} (also commonly known as "pointings") with small rectangles representing CCDs. \texttt{Patches} are represented by black dashed lines. One \texttt{Tract} typically contains xx  \texttt{Patches}.}
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2--m Subaru telescope,
    the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broad bands
    ($grizy$; Kawanomoto\etal in prep.).
    The Deep (four separated fields; ${\sim}27$ deg$^2$) and UltraDeep (two separated
    fields; ${\sim}3.5$ deg$^2$) layers use a few additional narrow-band filters
    and employ a slightly different surveying strategy.
    Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the
    HSC collaborators.

    The HSC camera (\citealt{Miyazaki2012}) is made up of 124 full-depletion thick
    CCDs: 112 for science and another 12 for guiding and focusing.
    The camera has a circular FoV with a 1.5 deg diameter.
    Each CCD contains 2048$\times$4096 pixels and the sizes of pixels are 0.168\asec{}.

    In February 2017, the HSC collaboration released the first 1.7 years of data to
    the public (DR1;
    \citealt{HSCDR1})\footnote{\texttt{https://hsc-release.mtk.nao.ac.jp }}.
    For our work, we focused on data from the Wide layer as they relate to key
    scientific goals of the HSC survey, which include weak lensing cosmology, galaxy evolution, and studies of galaxy clusters.  The Wide layer data in DR1 corresponds to ${\sim}108$ deg$^2$ spread over 
   six fields (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purposes.}.
    Except for the HECTOMAP field, the regions are all close to the equator.
    In the Wide layer, the $g$ and $r$ bands have 10 minute exposures broken into four
    dithers.  The  $i$, $z$, and $y$ bands have 20 minute exposures broken into six dithers. The survey prioritizes the observations so that the $i$-band has the best seeing conditions to improve galaxy shape measurements for weak lensing science. The  $i$ band data in the Wide layer reach a $5\sigma$ point source limiting magnitude of  $i{\sim} 26.4$ mag  and have a median seeing with FWHM${\sim}0.6$\asec{}. \citealt{HSCDR1} provides details on the first data release and data status.

@@

The HSC data are reduced using a pipeline that builds on the prototype pipeline being designed by the Large Synoptic Survey Telescope’s Data Management system (\citealt{Ivezic2008, Axelrod2010,
    Juric2015}) and is described in Bosch\etal (in prep.). DR1 data are reduced by \hscpipe{} \texttt{v4.0.5}. Because\synpipe{} is intrinsically connected to the complex data reduction
    processes in \hscpipe{}, we briefly introduce the main steps below, and we introduce a few key HSC/LSST terms.

@@

        \item \textbf{Single-\texttt{Visit~}Processing}:
            Each individual exposure is called a \term{Visit} and is assigned
            an even integer.
            After initial data screening (considering the background level, seeing, and transparency
            Furusawa\etal in prep.), \hscpipe{} detrends these data (subtraction
            of overscan, bias, and dark; flatfielding), \alexie{xxxxx} generates variance and mask
            images, subtracts the background, and provides initial astrometric and
            photometric calibrations. \synpipe{} uses the spatially varying PSF models, photometric zeropoints, and the World Coordinate System (WCS; \citealt{WCS1, WCS2})
            corrected for optical distortion provided by \hscpipe{}.
        \item \textbf{Multi-\visit{} Processing}:
            After single-\visit{} processing, \hscpipe{} warps and mosaics the
            reduced CCD images into much deeper \coadd{} images while improving
            the astrometric and photometric calibrations via processes similar to
            the \"{u}ber-calibration in the Sloan Digital Sky Survey (SDSS)
            \citep{Padmanabhan2008}.
            \textbf{\synpipe{} will use these improved calibrations.}
            \hscpipe{} organizes these \coadd{} images into equiareal rectangular
            regions, or \tracts{}, which are predefined as iso-latitude tessellations.
            One \tract{} covers approximately $1.7\times 1.7$ degrees$^2$ and
            adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
            Each \tract{} is further divided into $9\times9$ \texttt{Patches}.
            A \texttt{Patch} is a $4200\times4200$ pixels rectangular region, and
            adjacent \texttt{Patches} overlap each other by 100 pixels.   
        \item \textbf{Multi-band Measurements}:
            To achieve consistent photometry across all filters, \hscpipe{} first
            detects and deblends objects on \coadd{} images in each band
            independently (the \unforced{} measurements).
            The collection of above-threshold pixels for each object is referred to as
            a \texttt{footprint}.
            \hscpipe{} merges the \texttt{footprints} and flux peaks in the different
            bands and then selects a reference band for each object based on its $S/N$ in each band (usually this corresponds to the $i$-band).  Centroids, shapes, and other non-amplitude parameters are then fixed to  the values from the reference band. \hscpipe{} then performs \forced{} photometry using these fixed quantities. The goal of the  \forced{} photometry step is to generate accurate colors.
        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain various types of photometry measurements (see \citealt{HSCDR1} for details). Here, we focus on characterizing the the \forced{} \texttt{psf} and \cmodel{}
            photometry. The
            \texttt{psf} photometry should provide the most appropriate magnitudes and
            colors for point sources. The  \cmodel{} should be used for galaxies. The HSC  \cmodel{} algorithm is described in Bosch\etal, in prep. and is an  improved version of the SDSS \cmodel{} magnitude (\citealt{Lupton2001, Abazajian2004}). The HSC  \cmodel{} fits objects using both a de Vaucouleurs and an exponential profiles taking into account the smearing by the PSF.  \cmodel{} then linearly combines the two results to find the best fit to the galaxy image. \cmodel{} magnitudes are designed to yield accurate fluxes and colors for galaxies. Star--galaxy separation is performed based on
            the difference between \texttt{psf} and \cmodel{}{} magnitudes.
    \end{enumerate}

    DR1 data quality has been vetted in \citet{HSCDR1} by cross-checking
    with the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1
    imaging survey (\citealt{Schlafly2012, Tonry2012, Magnier2013}) to examine the
    behavior of the stellar sequence.
    Generally speaking, the PSF photometry is accurate at the 1--2\% level \alexie{only for bright stars}, and the
    astrometry is accurate to ${\sim}10$ and 40 max internally and externally.

@@

%% ------------------------------------------------------------------------------------ %%
\subsection{Design}
    \label{ssec:design}

    \hscpipe{} is a complex data reduction pipeline that still faces many challenges
    and is under active development.
    Unlike most photometric pipelines on the market, it involves high-level reduction
    processes that produce not only deep \coadd{} images but also a series of
    science-ready catalogs. To perform tests of the  data products that result from \hscpipe{},  \synpipe{} is designed to satisfies a few basic standards:

@@

        \item \textbf{Realistic Images}:
            Instead of using a fully generative approach to simulate full HSC-like
            images from the ground up (e.g., \citealt{Chang2015}), \synpipe{} injects
            synthetic objects into real HSC images so that all the realistic
            features of the real data (e.g., blended objects; proximity to bright
            objects, bleeding trails, other optical artifacts can be included in the
            test.
            The impact of these features can be important for studies that care about completeness and the selection
            function.
            In \synpipe{}, point sources are simulated using the HSC PSF model,
            and a realistic galaxy model is created by the modular galaxy image
            simulation toolkit, \galsim{} (\citealt{Rowe2015})
            \footnote{\texttt{https://github.com/GalSim-developers/GalSim}}.

        \item \textbf{Authentic Data Processing}:
            To follow the data reduction process as realistically as possible, we choose to
            start from the single-\visit{} images instead of directly putting synthetic
            objects on the final \coadd{} images (e.g., \citealt{Suchyta2016}).
            Through this approach, subtle effects like seeing differences among
            \visits{} and small errors in astrometric calibration can be taken
            into account.
            Every synthetic object will experience all the steps we would use for a real object: detection, deblending, stacking, and measurement.
            This can be important for challenging tasks like WL measurements
            or the detection of high-$z$ galaxies.
            The downside of this choice is that it slows down the overall run-time because we need to inject synthetic objects into all the \visits{} that contribute to a \tract{}.
        \item \textbf{Flexible Capabilities}: \synpipe{} is designed to be flexible enough to be useful for HSC users with a range of scientific goals.
            We provide default catalogs to generate samples of synthetic stars
            and galaxies with realistic magnitudes and color distributions along with
            tools to help the user work on HSC DR1 data. However, \synpipe{} also easily allows users to  design and use their own custom made input catalogs.
            \synpipe{} is already being used in a wide range of
            scientific applications (see Section \ref{sec:summary} for details).
